Thesis Proposal

### 2019-10-02 ThesisProposal.Rmd
Added figure: Impression of ShinyMICE

---
title: "Thesis Proposal"
author: "Hanne Oberman (4216318)"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  #word_document: default
  pdf_document:
    fig_caption: yes
subtitle: Methodology and Statistics for the Behavioural, Biomedical and Social Sciences
bibliography: ThesisProposal.bib
---

@@

The *missing data model* assumption entails that missing values are distributed similar to observed values, after correcting for covariates ^[@buur18]. Differences between observed and imputed data can be evaluated by plotting conditional distributions ^[@abay08]. This procedure currently lacks an interactive interface and statistical tests to quantify the relations with covariates. Moreover, model fit could be assessed using *over-imputation* ^[@buur18] or *double robustness* ^[bang05].

@@

Subsequently, I will implement this and other evaluation measures in `ShinyMICE`. The application will at least contain modules for: sensitivity analyses; data visualizations (e.g., scatter-plots, densities, cross-tabulations); and statistical evaluations of relations between variables pre- versus post-imputation (i.e., $\chi^2$-tests or t-tests).

>>>>

---
title: "Thesis Proposal"
author: "Hanne Oberman (4216318)"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  #word_document: default
  pdf_document:
    fig_caption: yes
subtitle: Methodology and Statistics for the Behavioural, Biomedical and Social Sciences
bibliography: ThesisProposal.bib
biblio-style: "apalike"
---

@@

The *missing data model* assumption entails that missing values are distributed similar to observed values, after correcting for covariates ^[@buur18]. Differences between observed and imputed data can be evaluated by plotting conditional distributions ^[@abay08]. This procedure currently lacks an interactive interface and statistical tests to quantify the relations with covariates. Moreover, model fit could be assessed using *over-imputation* ^[@buur18] or *double robustness* ^[@bang05].

@@

Subsequently, I will implement this and other evaluation measures in `ShinyMICE`, see Figure 1. The application will at least contain methodology for: sensitivity analyses; data visualizations (e.g., scatter-plots, densities, cross-tabulations); and statistical evaluations of relations between variables pre- versus post-imputation (i.e., $\chi^2$-tests or t-tests).

![Preliminary impression of the interactive `ShinyMICE` user interface](Figures/Impression.png)
